Energy and the CES production function

### 2015-09-21 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
tweaking output elasticities plots and removing ...TriPlot()

<<output_elasticities_graph_ternary, fig.pos="H", fig.align="center", fig.width=6.5, fig.height=2.3, fig.cap="Ternary graph of output elasticities~($\\alpha$). This version shows all Unadjusted and Quality-adjusted points on the same graph. Perhaps it is easier to see the effect of quality-adjustment of data this way.">>=
p <- triPlot(
  data=
    AllCoeffs %>% filter(model == "CES") %>%
    mutate( nest = plyr::mapvalues(nest, 
                                   from=c("kle", "lek", "ekl"), 
                                   to=c("(kl)e", "(le)k", "(ek)l")),
            Model = interaction(nest, CSP, sep = " ", drop=TRUE),
            Inputs = flavor
            ), 
  grid_lines = 5,
  labels = c("alpha[k]", "alpha[l]", "alpha[e]"),
  aes(x = alpha_1, y = alpha_2, z = alpha_3, 
      fill  = Model, 
      shape = Model,
      size = Model,
      color = Inputs)
  ) +
  labs(color = "Factors of production") +
  facet_grid(. ~ Country)
  model_points_style(p)
@

<<output_elasticities_graph_ternary_2, fig.pos="H", fig.align="center", fig.width=6.5, fig.height=4.1, fig.cap="Ternary graph of output elasticities~($\\alpha$). This version splits the Unadjusted and Quality-adjusted values on their own graphs. This approach is parallel to the previous figures (historical data, fitted GDP, and residuals.">>=
p <- triPlot(
  data=
    AllCoeffs %>% filter(model == "CES") %>%
    mutate( nest = plyr::mapvalues(nest, 
                                   from=c("kle", "lek", "ekl"), 
                                   to=c("(kl)e", "(le)k", "(ek)l")),
            Model = interaction(nest, CSP, sep = " ", drop=TRUE),
            Inputs = flavor), 
  grid_lines = 5,
  labels = c("alpha[k]", "alpha[l]", "alpha[e]"),
  aes(x = alpha_1, y = alpha_2, z = alpha_3, 
      fill  = Model, 
      shape = Model,
      size = Model
      # color = Inputs
      )
  ) +
  facet_grid(Inputs ~ Country)

@@

<<>>=
require(tidyr)
ggplot(AllOE %>% 
         mutate(split = as.character(
           interaction(Country, flavor, lex.order = TRUE))) %>%
         gather(factor, elasticity, oe1, oe2, oe3), aes(x=Year)) +
  geom_line( 
    alpha = .5, size=1.8,
    aes(y = elasticity, 
        colour = factor, 
        linetype=flavor
    ) ) +
  facet_grid(nest ~ Country) +
  theme_minimal() 
@

>>>>

<<output_elasticities_graph_ternary, fig.pos="H", fig.align="center", fig.width=6.5, fig.height=2.3, fig.cap="Ternary graph of output elasticities~($\\alpha$). This version shows all Unadjusted and Quality-adjusted points on the same graph. Perhaps it is easier to see the effect of quality-adjustment of data this way.">>=
#p <- triPlot(
#  data=
p <-
  AllCoeffs %>% filter(model == "CES") %>%
    mutate( nest = plyr::mapvalues(nest, 
                                   from=c("kle", "lek", "ekl"), 
                                   to=c("(kl)e", "(le)k", "(ek)l")),
            Model = interaction(nest, CSP, sep = " ", drop=TRUE),
            Inputs = flavor
            ) %>%
  ggplot() +
  tri_theme() +
  tri_grid(grid_lines = 5) +
#  tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]")) +
  geom_tripoint(
    aes(
      x = alpha_1, y = alpha_2, z = alpha_3, 
      fill  = Model, 
      shape = Model,
      size = Model,
      color = Inputs)
  ) +
  labs(color = "Factors of production") +
  facet_grid(. ~ Country)

<<output_elasticities_graph_ternary_2, fig.pos="H", fig.align="center", fig.width=6.5, fig.height=4.1, fig.cap="Ternary graph of output elasticities~($\\alpha$). This version splits the Unadjusted and Quality-adjusted values on their own graphs. This approach is parallel to the previous figures (historical data, fitted GDP, and residuals.">>=
p <- 
#    triPlot(
#  data=
    AllCoeffs %>% filter(model == "CES") %>%
    mutate( nest = plyr::mapvalues(nest, 
                                   from=c("kle", "lek", "ekl"), 
                                   to=c("(kl)e", "(le)k", "(ek)l")),
            Model = interaction(nest, CSP, sep = " ", drop=TRUE),
            Inputs = flavor) %>%
    ggplot() +
    tri_theme() + 
    tri_grid(grid_lines = 5) +
    tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]")) +
    geom_tripoint(
      aes(
        x = alpha_1, y = alpha_2, z = alpha_3, 
        fill  = Model, 
        shape = Model,
        size = Model
      # color = Inputs
      )
  ) +
  facet_grid(Inputs ~ Country)

@@

<<>>=
require(tidyr)
AllOE %>% 
  mutate(split =
           as.character(
             interaction(
               factor(flavor, labels = c("QA", "UA")), 
               factor(nest, 
                      labels = c("(ek)l", "kl", "(kl)e", "(le)k")), 
               sep = ", ",
               lex.order = FALSE ) )
  ) %>%
  gather(factor, elasticity, oe1, oe2, oe3) %>%
  mutate(
    split2 = relevelFactor(
      factor(split), 
      paste( rep(c("UA", "QA"), times = 4 ), 
             rep(c("kl", "(kl)e", "(le)k", "(ek)l"), each=2),
             sep=", ")
    )
  ) %>%
  ggplot(aes(x=Year)) + 
  geom_line( 
    alpha = .8, # size=1.0,
    aes(y = elasticity, 
        colour = factor,
        linetype=factor,
        size = factor
    ) ) +
  facet_grid(split2 ~ Country) +
  scale_color_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c("black", "black", "gray70")
  ) +
  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
  scale_size_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values = c(.9, .9, .6)) +
  scale_linetype_manual( 
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c(2,3,1) ) + 
  xy_theme()
